---
title: "All Cohorts Combined (101 Students)"

output: 
  html_document:
    theme: flatly
    toc: true
    toc_depth: 1
    toc_float:
      collapsed: true
    code_folding: hide
    
---
This group of 101 students is made up 5 cohorts who completed our materials between fall of 2016 and spring of 2018. These cohorts include: 14 community college students from fall 2016, 25 high school students from fall 2016, 19 high school students from summer 2017, 4 high school students from fall 2017, and 39 community college students from fall 2017 - spring 2018. The data from these cohorts can be combined because all 5 cohorts completed the same materials (with the exception of a few minor changes that will be documented in the manuscript currently in preparation) within similar time frames. All cohorts except the 39 community college students from fall 2017 - spring 2018 completed an immediate intervention study with no comparison group. Combining the data from all cohorts allows us to look at questions that don't depend on the immediate vs. delayed intervention framework with a higher degree of power. 

The code in the following analyses uses the following data frames: pretest.rds, lesson.rds, posttestAll.rds. The raw data can be downloaded from the "Materials" tab, and the process used to get the raw data into the pretest.rds, lesson.rds, posttestAll.rds format can be found in the "Data Process" tab. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Which TI problems were most difficult?

We looked at the pattern of performance on each of the 20 types of trigonometric identity problems, broken down into 3 groups - bottom, middle, top - based on performance on TI1. 
```{r,message=FALSE,fig.width=12,fig.height=7,warning=FALSE}
library(ggplot2)
library(dplyr)
library(data.table)
library(DT)
library(jsonlite)
library(tidyr)
library(reshape2) 

allTrigID <- readRDS("posttestAll.rds")

sin <- function(degree){
  round(base::sin(degree/180*pi),digits=4)
}

cos <- function(degree){
  round(base::cos(degree/180*pi),digits=4)
}

conjunctionJunction <- function(stim, theta) {
  evalStim <- eval(parse(text=stim))
  for(func in c('sin', 'cos')){
    for( sign in c('', '-')) {
      testAnswer = eval(parse(text=paste0(sign, func, "(", theta, ")")))
      if(isTRUE(all.equal(evalStim, testAnswer, tolerance = 0.01))) {
        return(paste0(sign, func))
      }
    }
  }
  return("")
} 

allTrigID$correctAnswer <- mapply(conjunctionJunction, allTrigID$stimulus, allTrigID$theta)


allTrigID2 <- separate(allTrigID, response, c("res.sign", "res.func"), sep="(?<=-)", remove = FALSE)
allTrigID2$res.func <- ifelse(allTrigID2$res.sign=="sin" | allTrigID2$res.sign=="cos",allTrigID2$res.sign,allTrigID2$res.func)
allTrigID2$res.sign <- ifelse(allTrigID2$res.sign=="sin" | allTrigID2$res.sign=="cos","+",allTrigID2$res.sign)


allTrigID2 <- separate(allTrigID2, correctAnswer, c("ans.sign", "ans.func"), sep="(?<=-)", remove = FALSE)
allTrigID2$ans.func <- ifelse(allTrigID2$ans.sign=="sin" | allTrigID2$ans.sign=="cos",allTrigID2$ans.sign,allTrigID2$ans.func)
allTrigID2$ans.sign <- ifelse(allTrigID2$ans.sign=="sin" | allTrigID2$ans.sign=="cos","+",allTrigID2$ans.sign)

allTrigID2$error <- ifelse(allTrigID2$res.sign!=allTrigID2$ans.sign & allTrigID2$res.func!=allTrigID2$ans.func, "Both wrong",
                    ifelse(allTrigID2$res.sign!=allTrigID2$ans.sign, "Wrong sign",
                    ifelse(allTrigID2$res.func!=allTrigID2$ans.func, "Wrong function",
                           "Correct")))

d <- allTrigID2 %>%
  group_by(func,xsign,delta) %>%
  summarize(acc=mean(correct)) %>%
  as.data.frame


d2 <- subset(allTrigID2, select = c(user, func, xsign, delta, correct, error, rt))

d2a <-
  d2 %>%
  group_by(user) %>%
  summarise(Average = round(mean(correct)*100,1))

d2a$third <- ntile(d2a$Average, 3) 

#create three data frames, one for each third of the data based on performance
bottom <- d2a[(d2a$third == 1),]
bottom <- bottom$user

middle <- d2a[(d2a$third == 2),]
middle <- middle$user

top <- d2a[(d2a$third == 3),]
top <- top$user

d2bottom <- d2 [d2$user %in% bottom,]
d2middle <- d2 [d2$user %in% middle,]
d2top <- d2 [d2$user %in% top,]

allTrigID2$signOrCorrect = (allTrigID2$error == "Correct") | (allTrigID2$error == "Wrong sign")
allTrigID2$funcOrCorrect = (allTrigID2$error == "Correct") | (allTrigID2$error == "Wrong function")

dbottom2 <- allTrigID2 [allTrigID2$user %in% bottom,]
dbottom = dbottom2 %>%
  group_by(func,xsign,delta) %>%
  summarize(acc=mean(correct)) %>%
  as.data.frame

dbottomFuncCorrect <- dbottom2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(signOrCorrect), count=n())

dbottomSignCorrect <- dbottom2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(funcOrCorrect), count=n())

dmiddle2 <- allTrigID2 [allTrigID2$user %in% middle,]
dmiddle = dmiddle2 %>%
  group_by(func,xsign,delta) %>%
  summarize(acc=mean(correct)) %>%
  as.data.frame

dmiddleFuncCorrect <- dmiddle2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(signOrCorrect), count=n())

dmiddleSignCorrect <- dmiddle2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(funcOrCorrect), count=n())

dtop2 <- allTrigID2 [allTrigID2$user %in% top,]
dtop = dtop2 %>%
  group_by(func,xsign,delta) %>%
  summarize(acc=mean(correct)) %>%
  as.data.frame

dtopFuncCorrect <- dtop2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(signOrCorrect), count=n())

dtopSignCorrect <- dtop2 %>%
  group_by(func,xsign,delta) %>%
  summarise(acc=mean(funcOrCorrect), count=n())

errorType <- function(i) {
  
  if(i=="bottom") {d2 <- d2bottom
                   d <- dbottom}
  if(i=="middle") {d2 <- d2middle
                   d <- dmiddle}
  if(i=="top") {d2 <- d2top
                d <- dtop}
  if(i=="bottomFuncCorrect") {d2 <- d2bottom
                d <- dbottomFuncCorrect}
  if(i=="bottomSignCorrect") {d2 <- d2bottom
                d <- dbottomSignCorrect}
  if(i=="middleFuncCorrect") {d2 <- d2middle
                d <- dmiddleFuncCorrect}
  if(i=="middleSignCorrect") {d2 <- d2middle
                d <- dmiddleSignCorrect}
  if(i=="topFuncCorrect") {d2 <- d2top
                d <- dtopFuncCorrect}
  if(i=="topSignCorrect") {d2 <- d2top
                d <- dtopSignCorrect}
  

d3 <- d2 %>%
  count(func,xsign,delta,error) %>%
  spread(error, n, fill = 0)

d4 <- merge(d, d3, by=c("func","xsign","delta"))


d4$delta = factor(d4$delta,levels=c(0,90,-90,180,-180))
d4$xsign = factor(d4$xsign,levels=c("+","-"))
#d$rule = factor(c(0,0,2,5,0, 4,0,1,0,4, 0,0,3,5,0, 4,0,1,0,4))
d4$rule = factor(c(0,0,3,0,5, 4,0,1,4,0, 0,0,2,0,5, 4,0,1,4,0))
d4$rule = factor(d4$rule,levels=c(1:5,0),labels=c('x±0=x','sin(–x)=–sin(x)','cos(–x)=cos(x)','func(x±180)=–func(x)','func(90–x)=opp(x)','Multiple/Other'))
#d$rule = factor(d$rule,levels=c(1:5,0),labels=c('$x\\pm0=x$','$\\sin(-x)=-\\sin(x)$','$\\cos(-x)=\\cos(x)$','$\\textrm{func}(x\\pm180)=-\\textrm{func}(x)$','$\\textrm{func}(90-x)=\\textrm{opp}(x)$','Multiple/Other'))


d4$signfunc = factor(interaction(d4$xsign,d4$func),levels=c('+.sin','+.cos','-.sin','-.cos'),labels=c('sin(+θ +/- Δ)','cos(+θ +/- Δ)','sin(-θ +/- Δ)','cos(-θ +/- Δ)'))

#d$signfunc = factor(interaction(d$xsign,d$func),levels=c('+.sin','+.cos','-.sin','-.cos'),labels=c('$\\sin(+\\theta \\pm \\Delta)$','$\\cos(+\\theta \\pm \\Delta)$','$\\sin(-\\theta \\pm \\Delta)$','$\\cos(-\\theta \\pm \\Delta)$'))

d4$delta = factor(d4$delta,levels=c(-180,-90,0,90,180))

d4 <- gather(d4, ErrorType, ErrorCount, -func, -xsign, -delta, -acc, -rule, -signfunc)

d4$ErrorType <- factor(d4$ErrorType, levels=c("Both wrong","Wrong function","Wrong sign","Correct"))

return(d4)

}


d4bottom <- errorType("bottom")
d4bottom$third <- "bottom"
d4middle <- errorType("middle")
d4middle$third <- "middle"
d4top <- errorType("top")
d4top$third <- "top"

##########################################
d4bottomFuncCorrect <- errorType("bottomFuncCorrect")
d4bottomFuncCorrect$third <- "bottom"
d4middleFuncCorrect <- errorType("middleFuncCorrect")
d4middleFuncCorrect$third <- "middle"
d4topFuncCorrect <- errorType("topFuncCorrect")
d4topFuncCorrect$third <- "top"


d4bottomSignCorrect <- errorType("bottomSignCorrect")
d4bottomSignCorrect$third <- "bottom"
d4middleSignCorrect <- errorType("middleSignCorrect")
d4middleSignCorrect$third <- "middle"
d4topSignCorrect <- errorType("topSignCorrect")
d4topSignCorrect$third <- "top"
##########################################

all <- rbind(d4bottom,d4middle,d4top)

ggplot(all,aes(delta,acc,fill=rule))+
  stat_summary(fun.y=mean,geom='bar') +
  facet_grid(third~signfunc)+theme_bw(20)+
  labs(x='Shift Δ',y='Accuracy',fill='Rule')+
  scale_fill_manual(values = c("#fb9a99","#a6cee3","#1f78b4", "#b2df8a","#F2ED2B","#999999")) + 
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), strip.background=element_blank())+scale_y_continuous(limits=c(0,1),labels = c(0,25,50,75,100))


```

The following graph presents the same results with the error responses broken down by whether the participant chose the alternative with the correct function but wrong signum, the incorrect function but correct signum, or neither the correct function nor signum. 
```{r,message=FALSE,fig.width=12,fig.height=7,warning=FALSE}
ggplot(all,aes(delta,ErrorCount,fill=ErrorType))+
  geom_bar(stat="identity")+
  facet_grid(third~signfunc)+theme_bw(20)+
  labs(x='Shift Δ',y='Count',fill='Error Type') 
```


# Which lesson problems are most difficult?

```{r,message=FALSE,warning=FALSE}
###find most frequently missed problems

lessonData <- readRDS("lesson.rds")
userIDs <- read.csv("combinedUserIDs.csv")
#exclude those who didn't meet threshold
noThreshold <- c(1719,1653,1735,1998,2038)
userIDs <- userIDs [! userIDs$TrigID %in% noThreshold,]
userIDs <- userIDs$TrigID

##only look at first attempt data
lessonData <- lessonData[lessonData$trialNumber==1,]

chs14 <- c(1:2,5:13,15:22,23:29,30:36)
ch56 <- c(37:45,47:57)

ch14Data <- lessonData [ lessonData$page_id %in% chs14,]
ch56Data <- lessonData [ lessonData$page_id %in% ch56,]



  lessonDataAverageAll <- 
    lessonData %>%
    group_by(user) %>%
    summarise(PercentCorrect = round(mean(firstCorrect)*100,1))
  
  lessonDataAverageCh14 <- 
    ch14Data %>%
    group_by(user) %>%
    summarise(PercentCorrect = round(mean(firstCorrect)*100,1))  
  
  lessonDataAverageCh56 <- 
    ch56Data %>%
    group_by(user) %>%
    summarise(PercentCorrect = round(mean(firstCorrect)*100,1))
  
LessonDataByProblem <-
  lessonData %>%
  group_by(order) %>%
  summarise(PercentCorrect = round(mean(firstCorrect)*100,1),
            MedianRT = round(median(rt)/1000,1))


##reduce dataset to problems less than 60% of students got correct
LessonDataLess60 <- LessonDataByProblem[LessonDataByProblem$PercentCorrect<60.1,]
lessthan60 <- LessonDataLess60$order

library(kableExtra)
mostMissedProblems <- read.csv("lessthan60.csv")
kable(mostMissedProblems) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


# What are the patterns of performance for the most frequently missed problems?
Below we show the accuracy results for the problems listed above broken down by the bottom, middle, and top thirds of the group as measured by TI1 performance. 
```{r,message=FALSE,warning=FALSE,fig.width=12,fig.height=8}

lessthan60Data <- lessonData [ lessonData$order %in% lessthan60,]

lessonBottom <- lessthan60Data [lessthan60Data$user %in% bottom,]
lessonMiddle <- lessthan60Data [lessthan60Data$user %in% middle,]
lessonTop <- lessthan60Data [lessthan60Data$user %in% top,]

lessthan60Bottom <-
  lessonBottom%>%
  group_by(order) %>%
  summarise(Bottom = round(mean(firstCorrect)*100,1))

lessthan60Middle <-
  lessonMiddle%>%
  group_by(order) %>%
  summarise(Middle = round(mean(firstCorrect)*100,1))

lessthan60Top <-
  lessonTop%>%
  group_by(order) %>%
  summarise(Top = round(mean(firstCorrect)*100,1))

lessonMerged <- merge(lessthan60Bottom,lessthan60Middle,by="order")
lessonMerged <- merge(lessonMerged,lessthan60Top,by="order")

lessonMergedLong <- gather(lessonMerged, third, percentCorrect, Bottom:Top, factor_key=TRUE)
lessonMergedLong$third <- factor(lessonMergedLong$third, levels=c("Bottom","Middle","Top"))

# ggplot(lessonMergedLong,aes(as.factor(problem),percentCorrect,fill=third))+
#   geom_bar(stat="identity",position="dodge") +
#   labs(x='Problem #',y='Percent Correct',fill='Third') 

ggplot(lessonMergedLong,aes(x=third,y=percentCorrect,fill=third))+
  geom_bar(stat="identity") +
  facet_wrap(~as.factor(order),ncol=6) +
  labs(x='Third',y='Percent Correct',fill='Third') +
  theme(strip.text.x = element_text(size = 14),axis.text.x = element_text(size = 10),legend.text=element_text(size=12))

```


